Sparsity Weak Lensing $3$-D Density Map Reconstruction: Reducing the line of sight smearing.

### 2020-11-28 doc/paper_ms_method_HSCY1/ms.tex
updating ms

\DeclareMathOperator{\arccosh}{arccosh}
\newcommand \redColor{\color{red}}
\renewcommand\labelenumi{(\roman{enumi})}
\renewcommand\theenumi\labelenumi

@@

\begin{document}
\title{Sparsity Weak Lensing $3$-D Density Map Reconstruction:
Reducing the line of sight smearing.}
%\author{Xiangchong Li}
%\affiliation{Department of Physics, University of Tokyo, Tokyo 113-0033, Japan}
%\affiliation{Kavli Institute for the Physics and Mathematics of the Universe (WPI),\\
%University of Tokyo, Kashiwa 277-8583, Japan}
%\author{Masamune Oguri}
%\affiliation{Department of Physics, University of Tokyo, Tokyo 113-0033, Japan}
%\affiliation{Kavli Institute for the Physics and Mathematics of the Universe (WPI),\\
%University of Tokyo, Kashiwa 277-8583, Japan}
%\affiliation{Research Center for the Early Universe, University of Tokyo, Tokyo 113-0033, Japan}
%\author{Wentao Luo}
%\affiliation{Kavli Institute for the Physics and Mathematics of the Universe (WPI),\\
%University of Tokyo, Kashiwa 277-8583, Japan}
%\author{HSC Collaboration}
%\noaffiliation
%\email{xiangchong.li@ipmu.jp}

@@

\begin{figure}
 \includegraphics[width=0.5\textwidth]{nfwlet-atom-1D.pdf}
 \caption{The $1$-D slices for smoothed pixelized basis atoms at $x=0$. The corresponding $2$-D profiles are
        shown in Figure \ref{fig-atoms2D}.} \label{fig-atoms1D}
\end{figure}

@@

\citet{LSS-massMap-Glimpse3D-Leonard2014} propose to use a derivative version
of $l^1$ lasso regulation ($C=\norm{x}^1_1$) to find a sparse solution in the
Starlets dictionary space \citep{Starlet-Starck2015}.
\citet{LSS-massMap-Glimpse3D-Leonard2014} apply a greedy coordinate descent
algorithm, which selects the steepest coordinate in each iteration, to find the
minima of a non-convex loss function penalized with the firm thresholding
function. \citet{LSS-massMap-Glimpse3D-Leonard2014} significantly reduce the
smearing along the line of sight. However, the stability of the non-convex
optimization and greedy coordinate descent algorithm has not been fully
justified. Moreover, the Starlets functions are not designed to model the
profile of clumpy mass in the universe.

@@

As shown in \citet{massMap-KS1993}, the shear field is related to the kappa
field at the same redshift plane via
\begin{equation}\label{eq-kappa2gamma}
\gamma_L(\vec{\theta},z_s) = \int  d^2 \theta' D(\vec{\theta}-\vec{\theta'}) \kappa(\vec{\theta'},z_s),
\end{equation}
where
\begin{equation}
D(\vec{\theta})=-\frac{1}{\pi}(\theta_1-i\theta_2)^{-2}.
\end{equation}
Here we denote the physical shear distortion field as $\gamma_L$ and we note
that the final observed shear measurements are also physical shear distortions
influenced by systematic errors from observatins. The systematic errors will be
discussed in Section \ref{subsec:method-Systematics}.

@@

The lasso algorithm uses $l^1$ norm of the projection coefficient field as to
regularize the modeling, and the estimator is defined as
\begin{equation}
\hat{x'}^{\rm{lasso}}=\argmin_{x} \left\{ \frac{1}{2}\norm{\Sigma^{-\frac{1}{2}}(\gamma- \mathbf{A'} x')}_2^2+ \lambda_{\rm{ls}} \norm{x'}^1_1\right\},
\end{equation}
where $\norm{\bigcdot}_1$ and $\norm{\bigcdot}_2$ refer to the $l^1$ norm and
$l^2$ norm, respectively.  $\lambda_{ls}$ denotes the penalization parameter
for the lasso estimation.

The lasso algorithm selects the parameters relevant to the measurements and
simultaneously estimates the value of the selected parameters.  However, it has
been shown by \citet{AdaLASSO-Zou2006} that when the column vectors of the
transforming matrix $\mathbf{A'}$ are highly correlated, the lasso cannot
select the relevant parameters from the parameter space consistently.
Moreover, the estimated parameters are biased due to the shrinkage in the lasso
regression. We note that, for the density map reconstruction problem, the
column vectors are highly correlated because, as shown in Figure
\ref{fig-corlensKer}, the lensing kernels for lenses at different redshifts are
highly correlated. Therefore, the lasso algorithm cannot select the consistent
mass in the line of sight direction, and the reconstructed mass suffers from
smears in the line of sight direction even in the absence of noise on shear
measurements.  Figure \ref{fig-lassoVsadaLasso} shows the reconstructions of a
single halo's mass map with halo mass equals $M_{200}=10^{15} ~h^{-1}M_{\odot}$
at redshift $0.35$. The noises on shear measurements are not included in the
simulation.  The left panel of Figure \ref{fig-lassoVsadaLasso} is the
reconstruction with the lasso algorithm, which shows a significant smear along
the line of sight.

@@

\begin{figure}[!t]
 \centering
 \includegraphics[width=0.45\textwidth]{peak_histograms.pdf}
 \caption{The histograms of detected peak values from all of the simulations.
     The solid lines with different colors are the results of reconstructions
     with the NFW dictionary penalized with different regularization parameter:
     $\lambda=3.5,4.0,5.0$. The dashed lines are the results of reconstructions
     from pure noise fields.
    }\label{fig-peakHist}
\end{figure}

In this work, we apply the Fast Iterative Soft Thresholding Algorithm (FISTA) of
\citet{FISTA-Beck2009} to find the global minima of the adaptive lasso's loss
function.

The coefficients are initialized as $x_i^{(1)}=0$. According to the FISTA
algorithm, we iteratively update the projection coefficient field ($x$). In the
$n$'th iteration, a temporary update is first calculated as
\begin{equation}
x'^{(n+1)}_{i}=\mathrm{ST}_{\lambda} \left(x'^{(n)}_{i} -\mu \partial_i G(x'^{(n)})\right),
\end{equation}
where $\mathrm{ST}$ is the soft thresholding function defined as
\begin{equation}
\mathrm{ST}_{\lambda} \left(x'\right) = \mathrm{sign} (x') \max \left(\abs{x'}-\lambda,0\right).
\end{equation}
$\mu$ is the step size of the gradient descent iteration.  $\partial_i
G(x'^{(n)})$ refers to the $i$'th element of the gradient vector of $G$ at
point $x'^{(n)}$:
\begin{equation}
\partial_i G(x'^{(n)})=\Sigma^{-1}_{\alpha\beta}\Re\left(A'^{*}_{\alpha i}(\gamma_{\beta}-A'_{\beta j}x'_{j})\right),
\end{equation}
where $\Re\left( \bullet \right)$ is the function returns the real part of the
input function. The FISTA algorithm requires an additional step amounting to a
weighted average between
$x'^{(n+1)}$ and $x'^{(n)}$:
\begin{equation}
\begin{split}
t^{(n+1)}&=\frac{1+\sqrt{1+4(t^{(n)})^2}}{2},\\
x'_{n+1} &\leftarrow x'^{(x+1)}+ \frac{t^{(n)}-1}{t^{(n+1)}}(x'^{(n+1)}-x'^{(n)}),
\end{split}
\end{equation}
where the relative weight is initialized as $t^{(1)}=1$.

Note that the FISTA algorithm converges as long as the gradient descent step
size $\mu$ satisfies
\begin{equation}
 0< \mu < \frac{1}{ \norm{\mathbf{A^{\dagger}} \mathbf{\Sigma}^{-1} \mathbf{A} }},
\end{equation}
where $\norm{\mathbf{A^{\dagger}} \mathbf{\Sigma}^{-1} \mathbf{A} }$ refers to
the spectrum norm of the matrix $\mathbf{A^{\dagger}} \mathbf{\Sigma}^{-1}
\mathbf{A}$. The spectral norm is estimated by simulating a large number of
random vectors with $l^2$ norms equal one with different realizations. The
matrix operator $\mathbf{A^{\dagger}} \mathbf{\Sigma}^{-1} \mathbf{A}$ is
subsequently applied to each random vector and get a corresponding transformed
vector. The spectral norm of the matrix $\mathbf{A^{\dagger}}
\mathbf{\Sigma}^{-1} \mathbf{A}$ is determined as the maximum $l^2$ norm of the
transformed vectors.

\subsubsection{The Algorithm}

The algorithm is described in Algorithm \ref{alg-1}.

\begin{algorithm}[H]
\renewcommand{\thealgorithm}{}
\label{alg-1}
\caption{Our Algorithm}
\begin{algorithmic}[1]
\INPUT $\gamma$: Pixelized complex $3$-D array of shear
\OUTPUT  $\delta$: $3$-D array of density contrast
\STATE Normalize column vectors of $\mathbf{A}$
\STATE Estimate step size $\mu$ and $\mathbf{\Sigma}$
\STATE \textbf{Initialization:}
\STATE $x'^{(1)} = 0$
\STATE $\hat{w}=1$, $\lambda=\lambda_{\rm{ls}}$
\STATE $t^{(1)}=1$,$i=1$, $j=1$
\WHILE{$j \leq 2$}
    \WHILE{$i \leq N_{\rm{iter}}$}
        \STATE $x'^{(n+1)}_{i}=\mathrm{ST}_{\hat{w}\lambda} \left(x'^{(n)}_{i} -\mu \partial_i G(x'^{(n)})\right)$
        \STATE $t^{(n+1)}=\frac{1+\sqrt{1+4(t^{(n)})^2}}{2}$
        \STATE $x'_{n+1} \leftarrow x'^{(x+1)}+ \frac{t^{(n)}-1}{t^{(n+1)}}(x'^{(n+1)}-x'^{(n)})$
        \STATE $i=i+1$
    \ENDWHILE
\STATE \textbf{Reinitialization:}
\STATE $\hat{w}=\abs{\hat{x'}^{\rm{lasso}}}^{-2}$, $\lambda=\lambda_{\rm{als}}$
\STATE $\hat{x'}^{(1)} = x'^{(N_{\rm{iter}})}$
\STATE $t^{(1)}=1$, $i=1$
\STATE $j=j+1$
\ENDWHILE
\STATE $\delta=\mathbf{\Phi}\mathcal{N}^{-\frac{1}{2}}x'^{(N_{\rm{iter}})}$
\end{algorithmic}
\end{algorithm}

@@

\begin{figure*}[!t]
\centering
\subfigure[NFW: $\lambda=3.5$]{
        \includezraphics{delta-1-7-pz-wn-NFW-falsepeakproblem.pdf}
        }
\subfigure[Point Mass: $\lambda=3.5$]{
        \includezraphics{delta-1-7-pz-wn-PM-falsepeakproblem.pdf}
        }
\subfigure[NFW: $\lambda=5.0$]{\includezraphics{
        delta-1-7-pz-wn-NFW_3-falsepeakproblem.pdf}
        }
\subfigure[Point Mass: $\lambda=5.0$]{
        \includezraphics{delta-1-7-pz-wn-PM_3-falsepeakproblem.pdf}
        }
\caption{The results of density maps reconstruction with the point mass
    dictionary (left) and the NFW dictionary (right) with $\lambda=3.5$ (upper)
    and $\lambda=5.0$ (lower). The input density map is from a NFW halo with
    mass $M_{200}=10^{15.02} ~h^{-1}M_{\odot}$ at redshift $0.164$. The
    vertical direction is the line of sight direction, and the lower boundaries
    and upper boundaries of the boxes are $0.01$ and $0.85$, respectively.
        } \label{fig-NFWvsPM}
\end{figure*}

@@

We sample halos in a two-dimensional redshift-mass plane. The redshift-mass
plane is evenly divided into eight redshift bins and eight mass bins. We
randomly shift the input halo redshifts and halo masses from the bins' centers
by a small amount. The concentration of the NFW halo is set to as a function of
the halo's mass ($M_{200}$) and redshift ($z_{h}$) according to
\citet{c-M_Magneticum-Ragagnin2019}
\begin{equation}
c_{h}=6.02\times(\frac{M_{200}}{10^{13} M_{\odot}})^{-0.12}(\frac{1.47}{1.+z_h})^{0.16}.
\end{equation}
The weak-lensing shear fields of these NFW halos are simulated according to
\citet{haloModel-TJ2003-3pt}. The shear distortions are applied to one hundred
realizations of galaxy catalogs with the HSC-like shape measurement error and
photo-$z$ uncertainty.

@@

In this subsection, we test the performance of our algorithm with the default
setup that models the matter density field with multi-scale NFW atoms. The
dictionary is constructed with three frames of different comoving scale radius:
$0.12~h^{-1}$ Mpc, $0.24~h^{-1}$ Mpc, and $0.36~h^{-1}$ Mpc.  The
truncation radius (concentration) is set to four times the scale radius for
the atoms in the dictionary. We test the algorithm with different
regularization parameters for the preliminary lasso ranging from $3.5$ to
$5.0$. The regularization parameter for the adaptive lasso is set to
$\lambda_{\rm{als}}=\lambda_{\rm{ls}}^{\gamma+1}$.

@@

After the reconstruction of each density field, we detect the peaks on the
density map. The stacked $2$-D histogram from all of the simulated boxes for
the offsets of the detected peak positions from the input halo is demonstrated
in the left panel of Figure \ref{fig-detoffsets}. For each simulation, we find
the positive peak closest to the input position (in the pixel unit), and if the
closest peak lay inside the region denoted with the dashed box in the left
panel of Figure \ref{fig-detoffsets}, we take it as a true detection of the
input halo. Other detected peaks, which include both positive and negative
peaks, are taken as false peak detections. The right panel of Figure
\ref{fig-detoffsets} shows the average redshift of true detections for each
halo.  The estimated redshifts are lower than the true redshifts by about
$0.03$ for halos in the low-redshift range ($z\leq 0.4$). For halos at
$0.4<z\leq 0.85$, the relative redshift bias is below $0.5\%$.

Figure \ref{fig-detFalsRateNFW} shows the detection rate (left panels) and the
number of false peaks per square degree (right panel) for each simulated halo.
The figure include results of different penalization parameters: $\lambda=3.5$
(upper panel) and $\lambda=5.0$ (lower panel).  We find that with the increase
of the penalization parameter, the detection rate decreases. On the other hand,
the number of false peaks also decreases.  Figure \ref{fig-peakHist} shows the
histograms, which are normalized by the number of simulations, for all
detected peaks with different penalization parameters. We also plot the
corresponding histograms for peaks detected from pure noise fields for
comparison. From the left panels of Figure \ref{fig-NFWvsPM}, which show the
$3$-D density maps reconstructed with different penalization parameters for a
halo with $M_{200}=10^{15.02} ~h^{-1}M_{\odot}$ at redshift $0.164$ , we also
find that the number of false detections significantly decreases as the
penalization parameter increases.

@@

In this subsection, we show the results for the setup, which substitutes the
default NFW dictionary with the point mass dictionary, to compare with the
default setup.  The regularization parameter for the preliminary lasso is set
to $3.5$ and $5.0$.  Inspired by \citet{structureAdaLasso-Pramanik2020}, which
propose to incorporate external group information into different adaptive lasso
penalization weights by setting the penalization weights for projection
coefficients in the same group to the average of the adaptive weights in this
group, we smooth the preliminary lasso estimation in each lens redshift bins
with a top-hat filter of comoving scale $0.25~h^{-1}$ Mpc, which is denoted as
$\hat{x}^{\rm{ls}}_{\rm{sm}}$ and the penalization weights are set to
$1/\abs{\hat{x}^{\rm{ls}}_{\rm{sm}}}^\gamma$.  The regularization parameter for
the adaptive lasso is set to $\lambda_{\rm{als}}=\lambda_{\rm{ls}}$.

@@

Figure \ref{fig-detFalsRatePM} shows the detection rate (left panels) and the
number of false peaks per square degree (right panel) for each simulated halo.
The figure includes results of different penalization parameters: $\lambda=3.5$
(upper panel) and $\lambda=5.0$ (lower panel). The right panels of Figure
\ref{fig-NFWvsPM} show the $3$-D density maps reconstructed with different
penalization parameters for a halo with $M_{200}=10^{15.02} ~h^{-1}M_{\odot}$
at redshift $0.164$. Comparing with the results for the NFW dictionary, we find
that the number of false peaks for the point mass dictionary is much larger
than that of the NFW dictionary. As demonstrated in the right panels of Figure
\ref{fig-NFWvsPM}, the reconstructions with the point mass dictionary tend to
assign masses to different redshifts in the neighboring region of the halo
center. Since the NFW atoms' profiles are more consistent with the input halo
profiles than the point mass profiles, the reconstructed structures from the
NFW dictionary are sparser than those from the point mass dictionary.

@@

\bibliographystyle{aasjournal}
\bibliography{citation}

>>>>

\DeclareMathOperator{\arccosh}{arccosh}
\newcommand \redColor{\color{red}}

\renewcommand\labelenumi{(\roman{enumi})}
\renewcommand\theenumi\labelenumi

@@

\begin{document}
\title{Sparsity Weak Lensing $3$-D Density Map Reconstruction:
Reducing the line of sight smearing.}
\author{Xiangchong Li}
\affiliation{Department of Physics, University of Tokyo, Tokyo 113-0033, Japan}
\affiliation{Kavli Institute for the Physics and Mathematics of the Universe (WPI),\\
University of Tokyo, Kashiwa 277-8583, Japan}
%\author{Masamune Oguri}
%\affiliation{Department of Physics, University of Tokyo, Tokyo 113-0033, Japan}
%\affiliation{Kavli Institute for the Physics and Mathematics of the Universe (WPI),\\
%University of Tokyo, Kashiwa 277-8583, Japan}
%\affiliation{Research Center for the Early Universe, University of Tokyo, Tokyo 113-0033, Japan}
%\author{Wentao Luo}
%\affiliation{Kavli Institute for the Physics and Mathematics of the Universe (WPI),\\
%University of Tokyo, Kashiwa 277-8583, Japan}
%\author{HSC Collaboration}
%\noaffiliation
%\email{xiangchong.li@ipmu.jp}

@@

\begin{figure}
 \includegraphics[width=0.5\textwidth]{nfwlet-atom-1D.pdf}
    \caption{The $1$-D slices for smoothed pixelized basis atoms at $x=0$. The
        corresponding $2$-D profiles are shown in Figure \ref{fig-atoms2D}.
        }
 \label{fig-atoms1D}
\end{figure}

@@

\citet{LSS-massMap-Glimpse3D-Leonard2014} propose to use a derivative version
of $l^1$ lasso regulation ($C=\norm{x}^1_1$) to find a sparse solution in the
Starlets dictionary space \citep{Starlet-Starck2015}.
\citet{LSS-massMap-Glimpse3D-Leonard2014} apply a greedy coordinate descent
algorithm, which selects the steepest coordinate in each iteration, to find the
minimum of a non-convex loss function penalized with the firm thresholding
function. \citet{LSS-massMap-Glimpse3D-Leonard2014} significantly reduce the
smearing along the line of sight. However, the stability of the non-convex
optimization and greedy coordinate descent algorithm has not been fully
justified. Moreover, the Starlets functions are not designed to model the
profile of clumpy mass in the universe.

@@

As shown in \citet{massMap-KS1993}, the shear field is related to the kappa
field at the same redshift plane via
\begin{equation}\label{eq-kappa2gamma}
\gamma_L(\vec{\theta},z_s) = \int  d^2 \theta' D(\vec{\theta}-\vec{\theta'}) \kappa(\vec{\theta'},z_s),
\end{equation}
where
\begin{equation}
D(\vec{\theta})=-\frac{1}{\pi}(\theta_1-i\theta_2)^{-2}.
\end{equation}
Here we denote the physical shear distortion field as $\gamma_L$ and we note
that the final observed shear measurements are influenced by systematic errors
from observations. The systematic errors will be discussed in Section
\ref{subsec:method-Systematics}.

@@

The lasso algorithm uses $l^1$ norm of the projection coefficient field to
regularize the modeling, and the estimator is defined as
\begin{equation}
\hat{x'}^{\rm{lasso}}=\argmin_{x} \left\{ \frac{1}{2}\norm{\Sigma^{-\frac{1}{2}}(\gamma- \mathbf{A'} x')}_2^2+ \lambda_{\rm{ls}} \norm{x'}^1_1\right\},
\end{equation}
where $\norm{\bigcdot}_1$ and $\norm{\bigcdot}_2$ refer to the $l^1$ norm and
$l^2$ norm, respectively.  $\lambda_{ls}$ denotes the penalization parameter
for the lasso estimation.

The lasso algorithm selects the parameters relevant to the measurements and
simultaneously estimates the value of the selected parameters.  However, it has
been shown by \citet{AdaLASSO-Zou2006} that when the column vectors of the
transforming matrix $\mathbf{A'}$ are highly correlated, the lasso cannot
select the relevant parameters from the parameter space consistently.
Moreover, the estimated parameters are biased due to the shrinkage in the lasso
regression. We note that, for the density map reconstruction problem, the
column vectors are highly correlated even in the absence of photometric
redshift uncertainties because, as shown in Figure \ref{fig-corlensKer}, the
lensing kernels for lenses at different redshifts are highly correlated.
Therefore, the lasso algorithm cannot select the consistent mass in the line of
sight direction, and the reconstructed mass suffers from smears in the line of
sight direction even in the absence of noise on shear measurements.  Figure
\ref{fig-lassoVsadaLasso} shows the reconstructions of a single halo's mass map
with halo mass equals $M_{200}=10^{15} ~h^{-1}M_{\odot}$ at redshift $0.35$.
The noises on shear measurements are not included in the simulation.  The left
panel of Figure \ref{fig-lassoVsadaLasso} is the reconstruction with the lasso
algorithm, which shows a significant smear along the line of sight.

@@

\begin{figure}[!t]
 \centering
 \includegraphics[width=0.45\textwidth]{peak_histograms.pdf}
 \caption{The histograms of detected peak values from all of the simulations.
     The solid lines with different colors are the results of reconstructions
     with the NFW dictionary penalized with different regularization parameters:
     $\lambda=3.5,4.0,5.0$. The dashed lines are the results of reconstructions
     from pure noise fields.
    }\label{fig-peakHist}
\end{figure}

\citet{FISTA-Beck2009} proposed the Fast Iterative Soft Thresholding Algorithm
(FISTA) to solve the lasso problem.  Since the lasso's loss function and the
adaptive lasso's loss function only differ in their penalization terms. The
FISTA is also applicable to the adaptive lasso problem. We apply the FISTA to
solve the preliminary lasso estimation and the final adaptive lasso estimation.

Here we start from the lasso preliminary estimation. The coefficients are
initialized as $x_i^{(1)}=0$. According to the FISTA algorithm, we iteratively
update the projection coefficient field ($x$). In the $n$'th iteration, a
temporary update is first calculated as
\begin{equation}
x'^{(n+1)}_{i}=\mathrm{ST}_{\lambda} \left(x'^{(n)}_{i} -\mu \partial_i G(x'^{(n)})\right),
\end{equation}
where $\mathrm{ST}$ is the soft thresholding function defined as
\begin{equation}
\mathrm{ST}_{\lambda} \left(x'\right) = \mathrm{sign} (x') \max \left(\abs{x'}-\lambda,0\right).
\end{equation}
The soft thresholding is a part of the lasso algorithm. It selects the
estimations with amplitude larger than $\lambda$, and shrink the estimations by
$\lambda$.
$\mu$ is the step size of the gradient descent iteration.  $\partial_i
G(x'^{(n)})$ refers to the $i$'th element of the gradient vector of $G$ at
point $x'^{(n)}$:
\begin{equation}
\partial_i G(x'^{(n)})=\Sigma^{-1}_{\alpha\beta}\Re\left(A'^{*}_{\alpha i}(\gamma_{\beta}-A'_{\beta j}x'_{j})\right),
\end{equation}
where $\Re\left( \bullet \right)$ is the function returns the real part of the
input function. The FISTA algorithm requires an additional update amounting to a
weighted average between
$x'^{(n+1)}$ and $x'^{(n)}$:
\begin{equation}
\begin{split}
t^{(n+1)}&=\frac{1+\sqrt{1+4(t^{(n)})^2}}{2},\\
x'^{(n+1)} &\leftarrow x'^{(x+1)}+ \frac{t^{(n)}-1}{t^{(n+1)}}(x'^{(n+1)}-x'^{(n)}),
\end{split}
\end{equation}
where the relative weight is initialized as $t^{(1)}=1$.

The FISTA algorithm converges as long as the gradient descent step size $\mu$
satisfies
\begin{equation}
 0< \mu < \frac{1}{ \norm{\mathbf{A^{\dagger}} \mathbf{\Sigma}^{-1} \mathbf{A} }},
\end{equation}
where $\norm{\mathbf{A^{\dagger}} \mathbf{\Sigma}^{-1} \mathbf{A} }$ refers to
the spectrum norm of the matrix $\mathbf{A^{\dagger}} \mathbf{\Sigma}^{-1}
\mathbf{A}$. The spectral norm is estimated by simulating a large number of
random vectors with $l^2$ norms equal one with different realizations. The
matrix operator $\mathbf{A^{\dagger}} \mathbf{\Sigma}^{-1} \mathbf{A}$ is
subsequently applied to each random vector and get a corresponding transformed
vector. The spectral norm of the matrix $\mathbf{A^{\dagger}}
\mathbf{\Sigma}^{-1} \mathbf{A}$ is determined as the maximum $l^2$ norm of the
transformed vectors.

As summarized in Algorithm \ref{alg-1}, we first initial the projection
coefficients as zero and use the FISTA algorithm to find the global minimum of
the lasso loss function. Such a global minimum is the preliminary estimation.
We then use the preliminary lasso estimation to weight the coefficients and
construct the adaptive lasso loss function. Finally, we set the preliminary
lasso estimation as the warm start of the adaptive lasso estimation and use the
FISTA algorithm again to find the adaptive lasso loss function's global minimum,
which is the final solution.

\begin{algorithm}[H]
\renewcommand{\thealgorithm}{}
\label{alg-1}
\caption{Our Algorithm}
\begin{algorithmic}[1]
\INPUT $\gamma$: Pixelized complex $3$-D array of shear
\OUTPUT  $\delta$: $3$-D array of density contrast
\STATE Normalize column vectors of $\mathbf{A}$
\STATE Estimate step size $\mu$ and $\mathbf{\Sigma}$
\STATE \textbf{Initialization:}
\STATE $x'^{(1)} = 0$
\STATE $\hat{w}=1$, $\lambda=\lambda_{\rm{ls}}$
\STATE $t^{(1)}=1$,$i=1$, $j=1$
\WHILE{$j \leq 2$}
    \WHILE{$i \leq N_{\rm{iter}}$}
        \STATE \# soft thresholding
        \STATE $x'^{(n+1)}_{i}=\mathrm{ST}_{\hat{w}\lambda} \left(x'^{(n)}_{i} -\mu \partial_i G(x'^{(n)})\right)$
        \STATE \# FISTA algorithm
        \STATE $t^{(n+1)}=\frac{1+\sqrt{1+4(t^{(n)})^2}}{2}$
        \STATE $x'^{(n+1)} \leftarrow x'^{(x+1)}+ \frac{t^{(n)}-1}{t^{(n+1)}}(x'^{(n+1)}-x'^{(n)})$
        \STATE $i=i+1$
    \ENDWHILE
\STATE \textbf{Reinitialization:}
\STATE $\hat{w}=\abs{\hat{x'}^{\rm{lasso}}}^{-2}$, $\lambda=\lambda_{\rm{als}}$
\STATE $\hat{x'}^{(1)} = x'^{(N_{\rm{iter}})}$
\STATE $t^{(1)}=1$, $i=1$
\STATE $j=j+1$
\ENDWHILE
\STATE $\delta=\mathbf{\Phi}\mathcal{N}^{-\frac{1}{2}}x'^{(N_{\rm{iter}})}$
\end{algorithmic}
\end{algorithm}

@@

\begin{figure*}[!t]
\centering
\subfigure[NFW: $\lambda=3.5$]{
        \includezraphics{delta-1-7-pz-wn-NFW-falsepeakproblem.pdf}
        }
\subfigure[Point Mass: $\lambda=3.5$]{
        \includezraphics{delta-1-7-pz-wn-PM-falsepeakproblem.pdf}
        }
\subfigure[NFW: $\lambda=5.0$]{\includezraphics{
        delta-1-7-pz-wn-NFW_3-falsepeakproblem.pdf}
        }
\subfigure[Point Mass: $\lambda=5.0$]{
        \includezraphics{delta-1-7-pz-wn-PM_3-falsepeakproblem.pdf}
        }
\caption{The results of density maps reconstruction with the point mass
    dictionary (left) and the NFW dictionary (right) with $\lambda=3.5$ (upper)
    and $\lambda=5.0$ (lower). The input density map is from a NFW halo with
    mass $M_{200}=10^{15.02} ~h^{-1}M_{\odot}$ at redshift $0.164$. The
    vertical direction is the line of sight direction, and the lower boundaries
    and upper boundaries of the boxes are $z=0.01$ and $z=0.85$, respectively.
        } \label{fig-NFWvsPM}
\end{figure*}

@@

We sample halos in a two-dimensional redshift-mass plane. The redshift-mass
plane is evenly divided into eight redshift bins and eight mass bins. We
randomly shift the input halo redshifts and halo masses from the bins' centers
by a small amount. The concentration of the NFW halo is set as a function of
the halo's mass ($M_{200}$) and redshift ($z_{h}$) according to
\citet{c-M_Magneticum-Ragagnin2019}
\begin{equation}
c_{h}=6.02\times(\frac{M_{200}}{10^{13} M_{\odot}})^{-0.12}(\frac{1.47}{1.+z_h})^{0.16}.
\end{equation}
The weak-lensing shear fields of these NFW halos are simulated according to
\citet{haloModel-TJ2003-3pt}. The shear distortions are applied to one hundred
realizations of galaxy catalogs with the HSC-like shape measurement error and
photo-$z$ uncertainty.

@@

In this subsection, we test the performance of our algorithm with the default
setup that models the matter density field with multi-scale NFW atoms. The
dictionary is constructed with three frames of different NFW comoving scale
radius: $0.12~h^{-1}$ Mpc, $0.24~h^{-1}$ Mpc, and $0.36~h^{-1}$ Mpc.  The
truncation radius (concentration) is set to four times the scale radius for the
atoms in the dictionary.

We test the algorithm with different regularization parameters for the
preliminary lasso estimation which range from $3.5$ to $5.0$. The
regularization parameter for the adaptive lasso is set to
$\lambda_{\rm{als}}=\lambda_{\rm{ls}}^{\tau+1}$.
Here, we note that both the preliminary lasso estimation and the final adaptive
estimation select the modes with signal to noise ratios (SNRs) greater than
$\lambda_{\rm{ls}}$ in each iteration. While the final adaptive lasso
estimation further enhances the growth of the modes with preliminary
estimations greater than $\lambda_{\rm{ls}}$.

@@

We detect the peaks on the density map after the reconstruction. The stacked
$2$-D histogram, from all of the simulations, for the offsets of the detected
peak positions from the input halos' positions is shown in the left panel of
Figure \ref{fig-detoffsets}.

For each simulation, we find the positive peak closest to the input position
(in the pixel unit), and if the closest peak lay inside the region denoted with
the dashed box in the left panel of Figure \ref{fig-detoffsets}, we take it as
a true peak detection of the input halo. Other detected peaks, which include both
positive and negative peaks, are taken as false peaks. The right
panel of Figure \ref{fig-detoffsets} shows the average redshift of true
detections for each halo. The estimated redshifts are lower than the true
redshifts by about $0.03$ for halos in the low-redshift range ($z\leq 0.4$).
For halos at $0.4<z\leq 0.85$, the relative redshift bias is below $0.5\%$.

Figure \ref{fig-detFalsRateNFW} shows the detection rate (left panels) and the
number of false peaks per square degree (right panel) for each simulated halo.
The figure include results of different penalization parameters: $\lambda=3.5$
(upper panel) and $\lambda=5.0$ (lower panel).  We find that with the increase
of the penalization parameter, the detection rate decreases. On the other hand,
the number of false peaks also decreases.

Figure \ref{fig-peakHist} shows the histograms, which are normalized by the
number of simulations, for all detected peaks with different penalization
parameters. We also plot the corresponding histograms for peaks detected from
pure noise fields for comparison. From the left panels of Figure
\ref{fig-NFWvsPM}, which show the $3$-D density maps reconstructed with
different penalization parameters for a halo with $M_{200}=10^{15.02}
~h^{-1}M_{\odot}$ at redshift $0.164$ , we also find that the number of false
peaks significantly decreases as the penalization parameter increases.

@@

In this subsection, we show the results for the setup, which substitutes the
default NFW dictionary with the point mass dictionary, to compare with the
default setup.  The regularization parameter for the preliminary lasso is set
to $3.5$ and $5.0$.  Inspired by \citet{structureAdaLasso-Pramanik2020}, which
propose to incorporate external group information into different adaptive lasso
penalization weights by setting the penalization weights for projection
coefficients in the same group to the average of the adaptive weights in this
group, we smooth the preliminary lasso estimation in each lens redshift bin
with a top-hat filter of comoving scale $0.25~h^{-1}$ Mpc. The smoothed
preliminary lasso estimation is denoted as $\hat{x}^{\rm{ls}}_{\rm{sm}}$, and
the penalization weights are set to $1/\abs{\hat{x}^{\rm{ls}}_{\rm{sm}}}^\tau$.
The regularization parameter for the adaptive lasso is set to
$\lambda_{\rm{als}}=\lambda_{\rm{ls}}$.

@@

Figure \ref{fig-detFalsRatePM} shows the detection rate (left panels) and the
number of false peaks per square degree (right panel) for each setup of halo
mass and redshift.
This figure includes results of different penalization parameters:
$\lambda=3.5$ (upper panel) and $\lambda=5.0$ (lower panel). The right panels
of Figure \ref{fig-NFWvsPM} show the $3$-D density maps reconstructed with
different penalization parameters for a halo with $M_{200}=10^{15.02}
~h^{-1}M_{\odot}$ at redshift $0.164$.
Comparing with the results of the NFW dictionary, we find that the number of
false peaks in the mass map reconstructed with the point mass dictionary is
much larger than the NFW dictionary.

As demonstrated in the right panels of Figure \ref{fig-NFWvsPM}, the mass
reconstructions with the point mass dictionary tend to assign masses to
several different redshift bins in the neighboring region of the halo center.
While the NFW dictionary produces consistent mass reconstructions.
Since the NFW atoms' profiles are more consistent with the mass profiles of the
input halos than the profile of a point mass, there are less false structures
reconstructed with the NFW dictionary.

@@

\section*{Acknowledgements}
We thank Yin Li and Jiaxin Han for useful discussion.

This work was supported by Global Science Graduate Course (GSGC) program of
University of Tokyo and JSPS KAKENHI (JP19J22222).
\bibliographystyle{aasjournal}
\bibliography{citation}
